Breakable Elastic-plastic Constraint for\\Rigid Body Simulation

### 2017-10-10 pdocs/thesis/epj-jcgt.tex
work on jcgt article

\paragraph{Joint breaking in one simulation step} High velocity collisions may cause joints to break within one step.
In such cases joints can cause too large impulse. Making simulation step smaller is not desired solution.
In this paper following procedure is suggested.

>>>>

\paragraph{Joint breaking in one simulation step} High velocity collisions may cause joints to break within one step.
In such cases joints can cause too large impulse as shown in  Figure~\ref{fig:tippingCar}.

\begin{figure}[htb]
  \centering
   \includegraphics[height=5cm]{figs/tippingCar1.png}
   \includegraphics[height=5cm]{figs/tippingCar2.png}
   \includegraphics[height=5cm]{figs/tippingCar3.png}
   \caption{\label{fig:tippingCar}
     Large impulse turns car over.}
\end{figure}
Making simulation step smaller is not desired solution.
In this paper following procedure is suggested.
